---
title: "Budget Report for PfS C1Y1"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
data <- read.csv("data.csv")
data <- merge(data,data.frame(state.abb, state.name), by.x="Grantee.Code", by.y="state.abb")
states <- map_data("state")
ourstates <- subset(states, region %in% tolower(data$state.name))
```

# Purpose
1. To determine where and how PfS funds have been utilized across all 16 Cohort 1 states in Year 1
2. To examine how funds are allocated to partners and activities across all 16 Cohort 1 states in Year 1
3. To make greater use of our administrative data by:
    + Informing CDC’s TA provided to PfS States
    + Providing information to inform future NOAs/NOFOs
  
# Methodology
* Utilized a budget analysis tool developed by Justin Uhd from DCPC.  Made alterations to the tool to fit the needs of PfS.
* Budget data from all 16 Cohort 1, Year 1 states were extracted from the Year 1 NOAs (09/01/2015 to 08/31/2016) and the proposed budget narratives for PfS Year 1 
* Key partners/contractors and activities were identified and reviewed by 2 reviewers
* An analysis of the budget data was conducted

# Limitations
* At this time, we only examined the budget data from PfS Cohort 1, Year 1
    + Cohort 2 operated on an 18-month grant period so side-by-side comparisons could be difficult
* Obtained limited FFRs due to files not being saved in the shared PDO file and the current changes/shifts within Grant Solutions
* Both the NOAs (actual) and budget narratives (proposed) were included
* The original version of the NOA for Utah was incorrect.  After obtaining the correct version, there was no breakdown of their approved budget (100% allocated to “Other”).  To prevent a skew in data, but to also include Utah, we utilized the data from their Budget Markup document.

#Evaluation Questions
1. How are PfS funds for Cohort 1, Year 1 allocated by states across budget categories?
2. Who have PfS Cohort 1, Year 1 grantees contracted with and what activities are those partners undertaking?
3. What is the breakdown of indirect vs. direct costs within contracts?
4. What funding remained unobligated at the end of the first PfS funded year?
5. Is there a difference in budget allocations between PHAB vs. non-PHAB accredited states?

##Evaluation Question 1
1. How are PfS funds for Cohort 1, Year 1 allocated by states across budget categories?

> - In Year 1, `r paste('$',formatC(sum(data$Total.Funding), big.mark=',', format = 'f', digits = 2))` was awarded to `r length(data$Grantee.Code)` PfS awardees with a median award of `r paste('$',formatC(median(data$Total.Funding), big.mark=',', format = 'f', digits = 2))`
```{r echo=FALSE}
ggplot() + 
  geom_polygon(data = states, aes(x = long, y = lat, group = group), fill = 'grey85', color = "grey45") +
  geom_polygon(data = ourstates, aes(x = long, y = lat, group = group), fill = 'lightblue', color = "blue") +
  coord_fixed(1.3) +
  guides(fill=FALSE)
```
> - Range: `r paste('$',formatC(min(data$Total.Funding), big.mark=',', format = 'f', digits = 2))` to `r paste('$',formatC(max(data$Total.Funding), big.mark=',', format = 'f', digits = 2))`
> - Median: `r paste('$',formatC(median(data$Total.Funding), big.mark=',', format = 'f', digits = 2))`
> - Mean: `r paste('$',formatC(mean(data$Total.Funding), big.mark=',', format = 'f', digits = 2))`

The PfS C1Y1 budgets were examined based on the **7 Office of Financial Resources (OFR) standard categories**

1. Contracts/Consultants: `r paste('$',formatC(sum(data$Contract.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Contract.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)
2. Total Personnel Cost (Salary and Fringe): `r paste('$',formatC(sum(data$Personnel_Salary.Amont,data$Fringe.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Personnel_Salary.Amont,data$Fringe.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)
3. Indirect Funding: `r paste('$',formatC(sum(data$Indirect.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Indirect.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)
4. Other: `r paste('$',formatC(sum(data$Other.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Other.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)
5. Travel: `r paste('$',formatC(sum(data$Travel.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Travel.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)
6. Supplies: `r paste('$',formatC(sum(data$Supplies.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Supplies.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)
7. Equipment: `r paste('$',formatC(sum(data$Equipment.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Equipment.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)

