---
title: "Budget Report for PfS C1Y1"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
data <- read.csv("data.csv")
data <- merge(data,data.frame(state.abb, state.name), by.x="Grantee.Code", by.y="state.abb")
states <- map_data("state")
ourstates <- subset(states, region %in% tolower(data$state.name))
```

# Purpose
1. To determine where and how PfS funds have been utilized across all 16 Cohort 1 states in Year 1
2. To examine how funds are allocated to partners and activities across all 16 Cohort 1 states in Year 1
3. To make greater use of our administrative data by:
    + Informing CDC’s TA provided to PfS States
    + Providing information to inform future NOAs/NOFOs
  
# Evaluation Questions
1. How are PfS funds for Cohort 1, Year 1 allocated by states across budget categories?
2. Who have PfS Cohort 1, Year 1 grantees contracted with and what activities are those partners undertaking?
3. What is the breakdown of indirect vs. direct costs within contracts?
4. What funding remained unobligated at the end of the first PfS funded year?
5. Is there a difference in budget allocations between PHAB vs. non-PHAB accredited states?

\newpage

## Evaluation Question 1
1. How are PfS funds for Cohort 1, Year 1 allocated by states across budget categories?

> - In Year 1, `r paste('$',formatC(sum(data$Total.Funding), big.mark=',', format = 'f', digits = 2))` was awarded to `r length(data$Grantee.Code)` PfS awardees with a median award of `r paste('$',formatC(median(data$Total.Funding), big.mark=',', format = 'f', digits = 2))`
```{r echo=FALSE}
ggplot() + 
  geom_polygon(data = states, aes(x = long, y = lat, group = group), fill = 'grey85', color = "grey45") +
  geom_polygon(data = ourstates, aes(x = long, y = lat, group = group), fill = 'lightblue', color = "blue") +
  coord_fixed(1.3) +
  guides(fill=FALSE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()
        )
```
> - Range: `r paste('$',formatC(min(data$Total.Funding), big.mark=',', format = 'f', digits = 2))` to `r paste('$',formatC(max(data$Total.Funding), big.mark=',', format = 'f', digits = 2))`
> - Median: `r paste('$',formatC(median(data$Total.Funding), big.mark=',', format = 'f', digits = 2))`
> - Mean: `r paste('$',formatC(mean(data$Total.Funding), big.mark=',', format = 'f', digits = 2))`

The PfS C1Y1 budgets were examined based on the **7 Office of Financial Resources (OFR) standard categories**

1. Contracts/Consultants: `r paste('$',formatC(sum(data$Contract.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Contract.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)
2. Total Personnel Cost (Salary and Fringe): `r paste('$',formatC(sum(data$Personnel_Salary.Amont,data$Fringe.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Personnel_Salary.Amont,data$Fringe.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)
3. Indirect Funding: `r paste('$',formatC(sum(data$Indirect.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Indirect.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)
4. Other: `r paste('$',formatC(sum(data$Other.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Other.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)
5. Travel: `r paste('$',formatC(sum(data$Travel.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Travel.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)
6. Supplies: `r paste('$',formatC(sum(data$Supplies.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Supplies.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)
7. Equipment: `r paste('$',formatC(sum(data$Equipment.Amount), big.mark=',', format = 'f', digits = 2))` (`r round((sum(data$Equipment.Amount)/sum(data$Total.Funding)*100),digits=2)`% of total)